Bayesian Inference from Time Series: Information Loss and the Whittle Likelihood

### 2018-03-21 doc/ms.tex

>>>>

If the {\em discrete} covariance function, defined for {\em integer} lag
$\tau$, is $C(\tau)$
then the PSD is a {\em continuous} function of angular frequency
$\omega \in (-\pi, \pi]$,
defined as
\begin{align}
S(\omega) &= \sum_\tau C(\tau)\exp\left(-i \omega \tau\right).
\end{align}
Since $C$ is necessarily an even function of $\tau$, the imaginary part of
$S(\omega)$ will be zero. In the Whittle likelihood, $S(\omega)$ is then
evaluated at a discrete set of points.
